\centering
\begin{center}
\Large{ACKNOWLEDGEMENTS}
\end{center}
\vspace{1em}
\normalsize
\justifying
\begin{flushleft}
\justifying
\par With immense pleasure and a deep sense of gratitude, I wish to express my sincere thanks to my supervisor \textbf{Dr. K. Anil Kumar}, School of Computer Science and Engineering, Vellore Institute of Technology (VIT), Vellore without his/her motivation and continuous encouragement, this research would not have been successfully completed.	 

\par I am grateful to the Chancellor of VIT, \textbf{Dr. G. Viswanathan}, the Vice Presidents, and the Vice Chancellor for motivating me to carry out research in the Vellore Institute of Technology. 

\par It would be no exaggeration to say that the Dean in-charge of SCOPE, \textbf{Prof. Jaisankar N}, was always available to clarify any queries and clear the doubts I had during the course of my project.
I would also like to acknowledge the role of the HoD, \textbf{Dr. G. Swati Jain}, who was instrumental in keeping me updated with all necessary formalities and posting all the required formats and document templates through the mail, which I was glad to have had. 

\par Finally, I would like to thank \textbf{Vellore Institute of Technology} for providing me with infrastructural facilities, a flexible choice and for supporting my research and execution related to the dissertation work.
\end{flushleft}
\paragraph{} 
\vspace{3cm}

\begin{flushleft}
Place: Vellore, \hspace{6cm} \textbf{Bollu Sai Likhitha \; (24MAI0083)} \linebreak
Date: 06-11-2025 \hspace{8cm} \linebreak    
\end{flushleft}

\pagebreak
